Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

%%%%%%%%%%%% 
\subsection{Initial Model Validation}\label{section:results_validation}
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also include no-flux across upper and lower borders. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a). The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region. \green{PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE ... ACTUALLY THIS IS NOT CORRECT AS THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY (AS INFERRED B4) OR IN PRESSURE, JUST A LARGE K AND P DISTRO ...} \red{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?}

>>>>

%%%%%%%%%%%% 
\subsection{Initial Model Validation}\label{section:results_validation}
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also include no-flux across upper and lower borders. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a). The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region. \red{(PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE (``The spatial discontinuities ... permeability region'') ... ACTUALLY THIS IS NOT CORRECT AS THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY OR IN PRESSURE, JUST A LARGE K AND P DISTRIBUTION ... IN ADDITION ...IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?)}
